The regularity of ODEs and thimble integrals \\ with respect to Borel summation

### 2024-03-26 exp-resurgence.tex
Finish rewriting Airy-Lucas thimble projection argument
It's hopefully finished, anyway.

Near each branch point $b$, let's fix a coordinate $\omega_b$ with $\zeta_b = \tfrac{1}{n} \omega_b^n$, where $2\pi n$ is the cone angle at $b$. This lets us label each direction at $b$ with an ``extended angle'' in $\R/2\pi n\Z$. Of course, there are $n$ different choices for $\omega_b$.
%
\subsubsection{Frequency}\label{transl-freq}
%
The translation structure also gives us an isomorphism $z \maps T^*_bB \to \C$ when $b \in B$ is an ordinary point, and an isomorphism $z \maps T^*_bB^{\otimes n} \to \C$ when $b$ is a branch point of cone angle $2\pi n$ \textcolor{orange}{[make it clear that $z$ is an almost-global chart on $T^*B$---for example, writing $z\colon T^*B\to\C^2$]}. At an ordinary point, we can define $z$ simply as the map
\begin{align*}
z \maps T^*_bB & \to \C \\
\lambda\big|_b & \mapsto 1.
\end{align*}
To get a definition that generalizes to branch points, though, it is worth taking a fancier point of view. Recall that $T^*_bB = \van_b / \van_b^2$, where $\van_b$ is the ideal of holomorphic functions that vanish at $b$. Observing that $(f + \van_b)^n$ lies within $f^n + \van_b^{n+1}$ for any $f \in \van_b$, we can identify $T^*_bB^{\otimes n}$ with $\van_b^n / \van_b^{n+1}$ for $n \ge 1$. When $b$ is an ordinary point, the function $\zeta_b$ defined in Section~\ref{transl:dir} represents a nonzero element of $\van_b / \van_b^2$: the cotangent vector $\lambda\big|_b$. In general, $\zeta_b$ represents a nonzero element of $\van_b^n / \van_b^{n+1}$, where $2\pi n$ is the cone angle at $b$. We define $z$ as the isomorphism
\begin{align*}
z \maps \van_b^n / \van_b^{n+1} & \to \C \\
\zeta_b + \van^{n+1} & \mapsto 1.
\end{align*}
When $b$ is a branch point, the coordinate $\omega_b$ we chose in Section~\ref{transl:dir} gives us an isomorphism
\begin{align*}
w_b \maps T^*_bB & \to \C \\
\omega_b + \van^2 & \mapsto 1
\end{align*}
that makes the diagram
\begin{center}
\begin{tikzcd}
T^*_bB^{\otimes n} \arrow[r,"z"] & \C \\
T^*_bB \arrow[u,"\blankbox^n"] \arrow[r,"w"'] & \C \arrow[u,"\blankbox^n"']
\end{tikzcd}
\end{center}
commute.
\subsubsection{Boundary}
\textcolor{red}{\textbf{Discuss the visual boundary, citing Lemma~3.1 of Dankwart's thesis \textit{On the large-scale geometry of flat surfaces} for the description of geodesics.}}
%
\subsubsection{The Laplace transform over an ordinary point}\label{laplace:ordinary}
Pick a local holomorphic function $\zeta$ on $B$ with $d\zeta = \lambda$, and an extended angle $\theta \in \R$. \textcolor{VioletRed}{[If we define ``translation parameter'' earlier, we can say:] Pick a translation parameter $\zeta$.} The {\em Laplace transform} $\laplace_\zeta^\theta$ turns a local holomorphic function $f$ on $B$ into a local holomorphic function on $T^*B$. When $b \in B$ is an ordinary point, $\laplace_\zeta^\theta f$ is defined on $T_b^*B$ by the formula
\begin{equation}\label{laplace:int}
\laplace_{\zeta}^\theta f\big|_b = \int_{\Gamma_{b}^\theta} e^{-z\zeta} f\,d\zeta,
\end{equation}
where $z$ is the frequency function and $\Gamma_{b}^\theta$ is the ray that leaves $b$ at angle $\theta$. We’ll use the shorthand $\laplace_{\zeta, b}^\theta f := \laplace_\zeta^\theta f \big|_{\zeta = b}$ throughout this document.

@@

\item With respect to the flat metric, $f$ is uniformly of exponential type $\Lambda$ along $\Gamma_b^\theta$, and is locally integrable throughout.\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{\Lambda+\varepsilon} $. We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.} Following \cite{reg-sing-volterra}, we require $f\in\singexp{\sigma}{\Lambda}(\Omega_b)$ with $\sigma>-1$.\footnote{The condition $\sigma>-1$ guarantees the integrability at $\zeta=b$.} The set $\Omega_b$ is a tubular neighbourhood of $\Gamma_b^\theta$. 
\item The value of $z$ is in the half-plane $H_{\theta}$ centered around the ray $e^{-i\theta} [0, \infty)$.

@@

\subsubsection{Rewriting as a modified Bessel $\frac{m}{n}$ equation}
We can distill the most interesting parts of the Airy-Lucas function by writing
\[ \widehat{\Ai}^{(j)}_{n, m-1}(y) = \textcolor{magenta}{\text{const.}}\,y^{{m/2}}\,K\big(\tfrac{2}{n} y^{n/2}\big), \]
where
\begin{equation}\label{integral:mod-bessel-rational-AL}
K_{m/n}(z) = \textcolor{magenta}{\text{const.}} \int_{\Lambda^\theta_j} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du.
\end{equation}
Saying that $\widehat{\Ai}^{(j)}_{n, m-1}$ satisfies the Airy-Lucas equation is equivalent to saying that $K$ satisfies the modified Bessel $\frac{m}{n}$ equation \textcolor{orange}{[Why put the order $m/n$ in the name? Is that standard?]}
\begin{equation}\label{eqn:mod-bessel-AL}
\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{m}{n} \big)^2 + z^2\big]\right] K = 0.
\end{equation}
In fact, as we will see in Section~\ref{contour-argument-AL}, $K$ is the modified Bessel function $K_{{m/n}}$.

@@

\subsubsection{Thimble projection reasoning for Airy-Lucas functions}\label{contour-argument-AL}
We follow the reasoning of the proof of Lemma~\ref{lem:thimble_proj_formula-proof}. We can recast integral~\eqref{integral:mod-bessel-rational-AL} into the $\zeta$ plane by setting $-\zeta = T_n(u)$, which implies that $-d\zeta = n U_{n-1}(u)\,du$. The critical point $u = \cos\big(\tfrac{j}{n}\pi\big)$ splits $\Lambda^\theta_j$ into two pieces: the {\em incoming} branch, where the orientation of the thimble runs toward the critical point, and the {\em outgoing} branch, where the orientation points away. Recalling that $\Lambda^\theta_j$ is a preimage of $\Gamma^\theta_{\zeta, \mp 1}$, we get \textcolor{magenta}{[mention that $\theta$ should be $\arg z$]}
\begin{align*}%%\label{integral:mod-bessel-rational-zeta}
K_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\Lambda^\theta_j} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
& = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \left[ \int_{\Gamma^\theta_{\mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_+)}{U_{n-1}(u_+)}\,d\zeta - \int_{\Gamma^\theta_{\mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_-)}{U_{n-1}(u_-)}\,d\zeta \right]
\end{align*}
where $u_-$ and $u_+$ are the lifts to the incoming and outgoing branches of $\Lambda^\theta_j$, respectively.
\begin{center}
\textcolor{orange}{[Draw the thimble in the $u$ plane]}
\end{center}

\color{DarkTurquoise}
Since the Chebyshev polynomial $T_n$ is defined by the identity $T_n(\cos(\phi)) = \cos(n\phi)$, we introduce a new variable $\phi$ with $u = \cos(\phi)$ and $-\zeta = \cos(n\phi)$. On the $\phi$ plane, which is an infinite branched cover of the $u$ plane, we can lift $\Lambda^\theta_j$ to the path $\tfrac{j}{n}\pi + i\R$. The incoming and outgoing branches lift to $\tfrac{j}{n}\pi - i[0, \infty)$ and $\tfrac{j}{n}\pi + i[0, \infty)$, respectively.
\begin{center}
\textcolor{orange}{[Draw the lifted thimble in the $\phi$ plane]}
\end{center}
We can now use identity~15.4.16 from \cite{dlmf} to write the integrand explicitly in terms of $\zeta$:
\begin{align*}
\frac{U_{m-1}(\cos(\phi))}{U_{n-1}(\cos(\phi))} &= \frac{\sin(m\phi)}{\sin(\phi)}\frac{\sin(\phi)}{\sin(n \phi)}\\
&= \frac{\sin(m\phi)}{\sin(n \phi)}\\
&= \frac{m}{n}\;{}_2F_1\Big(\frac{1}{2} - \frac{m}{2n}, \frac{1}{2} + \frac{m}{2n}; \frac{3}{2}; \sin^2(n \phi)\Big) \\
&= \frac{m}{n}\;{}_2F_1\Big(\frac{1}{2} - \frac{m}{2n}, \frac{1}{2} + \frac{m}{2n}; \frac{3}{2}; 1-\zeta^2\Big).
\end{align*}
This equation holds straightforwardly in the disk $|\phi| < \tfrac{\pi}{2n}$. As the value of $\phi$ goes along the real axis from $0$ to $\tfrac{\pi}{2n}$, the value of $\zeta$ goes along the real axis from $-1$ to $0$, at which point the hypergeometric function in the expression above becomes singular. To continue further, we have to dodge the singularity by pushing the value of $\zeta$ off the real axis. If we dodge into the lower half of the $\zeta$ plane, the value of $1 - \zeta^2$ loops counterclockwise around the singularity. In this case, as $\zeta$ continues from $0$ to $1$, we can use identity~15.2.3 of \cite{dlmf} to write
\begin{verify}
\begin{align*}
\frac{U_{m-1}(\cos(\phi))}{U_{n-1}(\cos(\phi))} & = \tfrac{m}{n}\;{}_2F_1\big(a, b; c; 1-\zeta^2\big) \\
& \quad + \tfrac{m}{n} \frac{2\pi i}{\Gamma(a) \Gamma(b)} (-\zeta^2)^{c-a-b} {}_2 F_1\big(c-a, c-b; c-a-b+1; \zeta^2\big) \\
& = \tfrac{m}{n}\;{}_2F_1\big(\tfrac{1}{2} - \tfrac{m}{2n}, \tfrac{1}{2} + \tfrac{m}{2n}; \tfrac{3}{2}; 1-\zeta^2\big) \\
& \quad + \tfrac{m}{n} \frac{2\pi i}{\Gamma\big(\tfrac{1}{2} - \tfrac{m}{2n}\big) \Gamma\big(\tfrac{1}{2} + \tfrac{m}{2n}\big)} (-\zeta^2)^{1/2} {}_2 F_1\big(1 + \tfrac{m}{2n}, 1 - \tfrac{m}{2n}; \tfrac{3}{2}; \zeta^2\big)
\end{align*}
\end{verify}
\begin{align*}
\frac{U_{m-1}(\cos(\phi))}{U_{n-1}(\cos(\phi))} & = \frac{m}{n}\;{}_2F_1\Big(\frac{1}{2} - \frac{m}{2n}, \frac{1}{2} + \frac{m}{2n}; \frac{3}{2}; 1-\zeta^2\Big) \\
& \quad - \frac{m}{n} \frac{2\pi \zeta}{\Gamma\big(\tfrac{1}{2} - \frac{m}{2n}\big) \Gamma\big(\frac{1}{2} + \frac{m}{2n}\big)} {}_2 F_1\Big(1 + \frac{m}{2n}, 1 - \frac{m}{2n}; \frac{3}{2}; \zeta^2\Big)
\end{align*}
in terms of the principal branch of the hypergeometric function.

@@

where in the second step we use the analytic continuation of the hypergeometric function \cite[Equation 15.2.3]{dlmf}.\color{black}

Finally, comparing this expression for $K_{m/n}$ with the expression for $v_1$ computed in Section \ref{pos-root} we notice that 
\begin{align*}
    K_{m/n}(z)=\frac{i}{2}\laplace_{\zeta,1}v_1 .
\end{align*}

\subsubsection{A flavor of resurgence: the Stokes phenomena in the position domain}\label{resurgence-AL}

>>>>

Near each branch point $b$, let's fix a coordinate $\omega_b$ with $\zeta_b = \tfrac{1}{n} \omega_b^n$, where $2\pi n$ is the cone angle at $b$. This lets us label each direction at $b$ with an ``extended angle'' in $\R/2\pi n\Z$. Of course, there are $n$ different choices for $\omega_b$.
%
\subsubsection{Frequency}\label{transl-freq}
%
The translation structure also gives us an isomorphism $z \maps T^*_bB \to \C$ when $b \in B$ is an ordinary point, and an isomorphism $z \maps T^*_bB^{\otimes n} \to \C$ when $b$ is a branch point of cone angle $2\pi n$ \textcolor{orange}{[make it clear that $z$ is an almost-global chart on $T^*B$---for example, writing $z\colon T^*B\to\C^2$]}. At an ordinary point, we can define $z$ simply as the map
\begin{align*}
z \maps T^*_bB & \to \C \\
\lambda\big|_b & \mapsto 1.
\end{align*}
To get a definition that generalizes to branch points, though, it is worth taking a fancier point of view. Recall that $T^*_bB = \van_b / \van_b^2$, where $\van_b$ is the ideal of holomorphic functions that vanish at $b$. Observing that $(f + \van_b)^n$ lies within $f^n + \van_b^{n+1}$ for any $f \in \van_b$, we can identify $T^*_bB^{\otimes n}$ with $\van_b^n / \van_b^{n+1}$ for $n \ge 1$. When $b$ is an ordinary point, the function $\zeta_b$ defined in Section~\ref{transl:dir} represents a nonzero element of $\van_b / \van_b^2$: the cotangent vector $\lambda\big|_b$. In general, $\zeta_b$ represents a nonzero element of $\van_b^n / \van_b^{n+1}$, where $2\pi n$ is the cone angle at $b$. We define $z$ as the isomorphism
\begin{align*}
z \maps \van_b^n / \van_b^{n+1} & \to \C \\
\zeta_b + \van^{n+1} & \mapsto 1.
\end{align*}
When $b$ is a branch point, the coordinate $\omega_b$ we chose in Section~\ref{transl:dir} gives us an isomorphism
\begin{align*}
w_b \maps T^*_bB & \to \C \\
\omega_b + \van^2 & \mapsto 1
\end{align*}
that makes the diagram
\begin{center}
\begin{tikzcd}
T^*_bB^{\otimes n} \arrow[r,"z"] & \C \\
T^*_bB \arrow[u,"\blankbox^n"] \arrow[r,"w"'] & \C \arrow[u,"\blankbox^n"']
\end{tikzcd}
\end{center}
commute.
\subsubsection{Boundary}
\textcolor{red}{\textbf{Discuss the visual boundary, citing Lemma~3.1 of Dankwart's thesis \textit{On the large-scale geometry of flat surfaces} for the description of geodesics.}}
%
\subsubsection{The Laplace transform over an ordinary point}\label{laplace:ordinary}
Pick a local holomorphic function $\zeta$ on $B$ with $d\zeta = \lambda$, and an extended angle $\theta \in \R$. \textcolor{VioletRed}{[If we define ``translation parameter'' earlier, we can say:] Pick a translation parameter $\zeta$.} The {\em Laplace transform} $\laplace_\zeta^\theta$ turns a local holomorphic function $f$ on $B$ into a local holomorphic function on $T^*B$. When $b \in B$ is an ordinary point, $\laplace_\zeta^\theta f$ is defined on $T_b^*B$ by the formula
\begin{equation}\label{laplace:int}
\laplace_{\zeta}^\theta f\big|_b = \int_{\Gamma_{b}^\theta} e^{-z\zeta} f\,d\zeta,
\end{equation}
where $z$ is the frequency function and $\Gamma_{b}^\theta$ is the ray that leaves $b$ at angle $\theta$. We’ll use the shorthand $\laplace_{\zeta, b}^\theta f := \laplace_\zeta^\theta f \big|_b$ throughout this document. \textcolor{magenta}{[Notation conflict: we also use $\laplace_{\zeta, \alpha}$ to represent starting at $\zeta = \alpha$, giving the starting point as a coordinate value instead of a point $b$.]}

@@

\item With respect to the flat metric, $f$ is uniformly of exponential type $\Lambda$ along $\Gamma_b^\theta$, and is locally integrable throughout.\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{\Lambda+\varepsilon} $. We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.} \textcolor{Pink}{[Revise]} Following \cite{reg-sing-volterra}, we require $f \in \singexp{\sigma}{\Lambda}(\Omega_b)$, with $\sigma>-1$.\footnote{The condition $\sigma>-1$ guarantees the integrability at $\zeta=b$.} The set $\Omega_b$ is a tubular neighbourhood of $\Gamma_b^\theta$. 
\item The value of $z$ is in the half-plane $H^{\theta}_\Lambda$ cut out by the inequality $\Re(e^{i\theta} z) > \Lambda$.

@@

\subsubsection{Rewriting as a modified Bessel $\frac{m}{n}$ equation}
We can distill the most interesting parts of the Airy-Lucas function by writing
\[ \widehat{\Ai}^{(j)}_{n, m-1}(y) = \textcolor{magenta}{\text{const.}}\,y^{{m/2}}\,K^{(j)}_{m/n}\big(\tfrac{2}{n} y^{n/2}\big), \]
where
\begin{equation}\label{integral:mod-bessel-rational-AL}
K^{(j)}_{m/n}(z) = \textcolor{magenta}{\text{const.}} \int_{\Lambda^\theta_j} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du.
\end{equation}
Saying that $\widehat{\Ai}^{(j)}_{n, m-1}$ satisfies the Airy-Lucas equation is equivalent to saying that $K$ satisfies the modified Bessel $\frac{m}{n}$ equation \textcolor{orange}{[Why put the order $m/n$ in the name? Is that standard?]}
\begin{equation}\label{eqn:mod-bessel-AL}
\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{m}{n} \big)^2 + z^2\big]\right] K = 0.
\end{equation}
In fact, as we will see in Section~\ref{contour-argument-AL}, $K$ is the modified Bessel function $K_{{m/n}}$.

@@

\subsubsection{Thimble projection reasoning for Airy-Lucas functions}\label{contour-argument-AL}
We follow the reasoning of the proof of Lemma~\ref{lem:thimble_proj_formula-proof}. We can recast integral~\eqref{integral:mod-bessel-rational-AL} into the $\zeta$ plane by setting $-\zeta = T_n(u)$, which implies that $-d\zeta = n U_{n-1}(u)\,du$. The critical point $u = \cos\big(\tfrac{j}{n}\pi\big)$ splits $\Lambda^\theta_j$ into two pieces: the {\em incoming} branch, where the orientation of the thimble runs toward the critical point, and the {\em outgoing} branch, where the orientation points away. Recalling that $\Lambda^\theta_j$ is a preimage of $\Gamma^\theta_{\zeta, \mp 1}$, we get \textcolor{magenta}{[mention that $\theta$ should be $\arg z$]}
\begin{align*}%%\label{integral:mod-bessel-rational-zeta}
K^{(j)}_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\Lambda^\theta_j} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
& = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \left[ \int_{\Gamma^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_+)}{U_{n-1}(u_+)}\,d\zeta - \int_{\Gamma^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_-)}{U_{n-1}(u_-)}\,d\zeta \right]
\end{align*}
where $u_-$ and $u_+$ are the lifts to the incoming and outgoing branches of $\Lambda^\theta_j$, respectively.
\begin{center}
\textcolor{orange}{[Draw the thimble in the $u$ plane]}
\end{center}

\color{DarkTurquoise}
Since the Chebyshev polynomial $T_n$ is defined by the identity $T_n(\cos(\phi)) = \cos(n\phi)$, we introduce a new variable $\phi$ with $u = \cos(\phi)$ and $-\zeta = \cos(n\phi)$. On the $\phi$ plane, which is an infinite branched cover of the $u$ plane, we can lift $\Lambda^\theta_j$ to the path $\tfrac{j}{n}\pi + i\R$. The incoming and outgoing branches lift to $\tfrac{j}{n}\pi - i[0, \infty)$ and $\tfrac{j}{n}\pi + i[0, \infty)$, respectively.
\begin{center}
\textcolor{orange}{[Draw the lifted thimble in the $\phi$ plane]}
\end{center}
We can now use identity~15.4.16 from \cite{dlmf} to write the integrand explicitly in terms of $\zeta$:
\begin{align*}
\frac{U_{m-1}(\cos(\phi))}{U_{n-1}(\cos(\phi))} &= \frac{\sin(m\phi)}{\sin(\phi)}\frac{\sin(\phi)}{\sin(n \phi)}\\
& = \frac{\sin(m\phi)}{\sin(n \phi)}\\
& = \frac{m}{n}\;{}_2F_1\left(\frac{1}{2} - \frac{m}{2n},\;\frac{1}{2} + \frac{m}{2n};\;\frac{3}{2};\;\sin^2(n \phi)\right) \\
& = \frac{m}{n}\;{}_2F_1\left(\frac{1}{2} - \frac{m}{2n},\;\frac{1}{2} + \frac{m}{2n};\;\frac{3}{2};\;1 - \zeta^2\right).
\end{align*}
Initially, we only know that this equation holds in the disk $|\phi| < \tfrac{\pi}{2n}$. However, observing that the left-hand side is meromorphic throughout the $\phi$ plane, we can deduce by analytic continuation that the equation holds throughout the $\phi$ plane.

Next, we simplify the integrand using identities 15.8.4 and 15.8.27--28 from \cite{dlmf}, which tell us that\begin{align*}
&{}_2F_1\left(\frac{1}{2} - \frac{m}{2n}, \frac{1}{2} + \frac{m}{2n}; \frac{3}{2}; 1 - \zeta^2\right) \\[3mm]
& =\; \hphantom{+} \frac{\pi}{\Gamma\left(1-\frac{m}{2n}\right) \Gamma\left(1 + \frac{m}{2n}\right)}\;{}_2F_1\left(\frac{1}{2} - \frac{m}{2n},\;\frac{1}{2} + \frac{m}{2n};\;\frac{1}{2};\;\zeta^2\right) \\
& \hphantom{=}\; - \frac{\pi \zeta}{\Gamma\left(\frac{1}{2} - \frac{m}{2n}\right) \Gamma\left(\frac{1}{2} + \frac{m}{2n}\right)}\;{}_2F_1\left(1 - \frac{m}{2n},\;1 + \frac{m}{2n};\;\frac{3}{2};\;\zeta^2\right) \\[3mm]
& =\; \hphantom{+ \frac{0}{0}}\;{}_2F_1\left(1 - \frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) + \hphantom{\frac{0}{0}}\;{}_2F_1\left(1-\frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) \\
& \hphantom{=}\; + \frac{1}{2}\;{}_2F_1\left(1-\frac{m}{n},\;1+\frac{m}{n};\;\frac{3}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) - \frac{1}{2}\;{}_2F_1\left(1-\frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) \\[3mm]
& =\; \hphantom{+} \frac{3}{2}\;{}_2F_1\left(1 - \frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\frac{1}{2} - \frac{\zeta}{2}\right) + \frac{1}{2}\;{}_2F_1\left(1 - \frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right)
\end{align*}
away from the line $\Re(\zeta) = 0$ and the rays $\Gamma^0_{\zeta,1}$ and $\Gamma^\pi_{\zeta,-1}$.

Returning to the projected thimble integral
\[ K^{(j)}_{m/n}(z) = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\Gamma^\theta_{\zeta, \mp 1}} e^{-z\zeta} \left[ \frac{U_{m-1}(u_+)}{U_{n-1}(u_+)} - \frac{U_{m-1}(u_-)}{U_{n-1}(u_-)} \right] d\zeta, \]
we can see the integrand as the variation of the function
\[ \frac{U_{m-1}(\cos(\phi))}{U_{n-1}(\cos(\phi))} = \frac{3m}{2n}\;{}_2F_1\left(1 - \frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\frac{1}{2} - \frac{\zeta}{2}\right) + \frac{m}{2n}\;{}_2F_1\left(1 - \frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) \]
across the branch cut $\Gamma^\theta_{\zeta, \mp 1}$. When $j$ is odd, only the second term will contribute to the jump, because the first term is regular at $\zeta = 1$. Similarly, when $j$ is even, only the first term will contribute to the jump. We can write the jump explicitly using identity~15.2.3 from \cite{dlmf}. For odd $j$, we have
\[ K^{(j)}_{m/n}(z) = -\frac{1}{2} \int_{\Gamma^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \frac{m}{n},\;\frac{1}{2} + \frac{m}{n};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta, \]
and for even $j$, we have \textcolor{magenta}{[check]}
\[ K^{(j)}_{m/n}(z) = -\frac{3}{2} \int_{\Gamma^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \frac{m}{n},\;\frac{1}{2} + \frac{m}{n};\;\frac{1}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) d\zeta. \]

Comparing the expressions above with the expressions for $v_{\pm 1}$ computed in Sections~\ref{pos-root}--\ref{neg-root}, we notice that
\[ K^{(j)}_{m/n}(z) = \begin{cases}
\frac{i}{2}\laplace_{\zeta, 1} v_1 & j \text{ odd} \\
\frac{i}{2}\laplace_{\zeta, -1} v_{-1} \;\textcolor{magenta}{\text{(?)}} & j \text{ even}.
\end{cases} \]

\color{GreenYellow}
This equation holds straightforwardly in the disk $|\phi| < \tfrac{\pi}{2n}$. As the value of $\phi$ goes along the real axis from $0$ to $\tfrac{\pi}{2n}$, the value of $\zeta$ goes along the real axis from $-1$ to $0$, at which point the hypergeometric function in the expression above becomes singular. To continue further, we have to dodge the singularity by pushing the value of $\zeta$ off the real axis. If we dodge into the lower half of the $\zeta$ plane, the value of $1 - \zeta^2$ loops counterclockwise around the singularity. In this case, as $\zeta$ continues from $0$ to $1$, we can use identity~15.2.3 of \cite{dlmf} to write
\begin{verify}
\begin{align*}
\frac{U_{m-1}(\cos(\phi))}{U_{n-1}(\cos(\phi))} & = \tfrac{m}{n}\;{}_2F_1\big(a, b; c; 1-\zeta^2\big) \\
& \quad + \tfrac{m}{n} \frac{2\pi i}{\Gamma(a) \Gamma(b)} (-\zeta^2)^{c-a-b} {}_2 F_1\big(c-a, c-b; c-a-b+1; \zeta^2\big) \\
& = \tfrac{m}{n}\;{}_2F_1\big(\tfrac{1}{2} - \tfrac{m}{2n}, \tfrac{1}{2} + \tfrac{m}{2n}; \tfrac{3}{2}; 1-\zeta^2\big) \\
& \quad + \tfrac{m}{n} \frac{2\pi i}{\Gamma\big(\tfrac{1}{2} - \tfrac{m}{2n}\big) \Gamma\big(\tfrac{1}{2} + \tfrac{m}{2n}\big)} (-\zeta^2)^{1/2} {}_2 F_1\big(1 + \tfrac{m}{2n}, 1 - \tfrac{m}{2n}; \tfrac{3}{2}; \zeta^2\big)
\end{align*}
\end{verify}
\begin{align*}
\frac{U_{m-1}(\cos(\phi))}{U_{n-1}(\cos(\phi))} & = \frac{m}{n}\;{}_2F_1\Big(\frac{1}{2} - \frac{m}{2n}, \frac{1}{2} + \frac{m}{2n}; \frac{3}{2}; 1-\zeta^2\Big) \\
& \quad - \frac{m}{n} \frac{2\pi \zeta}{\Gamma\big(\tfrac{1}{2} - \frac{m}{2n}\big) \Gamma\big(\frac{1}{2} + \frac{m}{2n}\big)} {}_2 F_1\Big(1 + \frac{m}{2n}, 1 - \frac{m}{2n}; \frac{3}{2}; \zeta^2\Big)
\end{align*}
in terms of the principal branch of the hypergeometric function.

@@

where in the second step we use the analytic continuation of the hypergeometric function \cite[Equation 15.2.3]{dlmf}.

Finally, comparing this expression for $K_{m/n}$ with the expression for $v_1$ computed in Section \ref{pos-root} we notice that 
\begin{align*}
K_{m/n}(z)=\frac{i}{2}\laplace_{\zeta,1}v_1 .
\end{align*}
\color{black}
%
\subsubsection{A flavor of resurgence: the Stokes phenomena in the position domain}\label{resurgence-AL}
%
In the previous sections, we have seen how to compute the Borel transform of a formal frame of solutions of the modified Bessel equation with parameter $m/n$ (Section \ref{confirmation-borel-regularity}) or equivalently of the asymptotic expansion of thimble integrals $K_{m/n}$ (Section \ref{contour-argument-AL}). In both cases we find 
\begin{align*}
    v_1(\zeta)= i \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)
\end{align*}
which has a fractional power singularity at $\zeta=1$. In addition, the hypergeometric function ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)$ is convergent at $\zeta=1$ therefore $v_1$ has the typical form of a \textit{singularity} in the formalism of \'Ecalle's resurgent functions. More precisely, we can consider ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)$ as a new holomorphic function (analytic continuation of a new germ at the origin), which has a branch cut singularity at $\zeta=-1$. Using equation \cite[15.2.3]{dlmf}, we can compute the analytic continuation of this germ at $\zeta=-1$: 
\begin{align*}
&{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}+i\varepsilon\right)-{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}-i\varepsilon\right)=\\
&=\frac{2\pi i}{\Gamma\big(\tfrac{1}{2}-\tfrac{m}{n}\big)\Gamma\big(\tfrac{1}{2}+\tfrac{m}{n}\big)} \left(-\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
&=2 i\cos(\pi m/n) \left(-\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
&=2\cos(\pi m/n) \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
&=2\cos(\pi m/n)\, \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} \left(-\frac{\zeta_{1}}{2}\right)^{1/2}\, {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right)
\end{align*}
Hence, we deduce  
\begin{equation}\label{resurgent-relation-1}
    v_1(\zeta+1+i\varepsilon)-v_1(\zeta+1+i\varepsilon)=2i \cos(\pi m/n)  v_{-1}(\zeta)
\end{equation}
namely, that the germ of the singularity at $\zeta=1$ knows about the germ of the singularity at $\zeta=-1$. This is an instance of \textit{resurgent functions}, introduced by \'Ecalle in \cite{EcalleI,EcalleII,EcalleIII}\footnote{If the reader is interested in resurgence, it may be useful to look at the following review \cite{diverg-resurg-i,Dorigoni,aniceto2019primer}.}. Although we’ll not discuss more about resurgence, we would like to point out that among the great advantages of resurgence (for instance compared to Borel summability) there are the \textit{formalism of singularities} and the \textit{Alien calculus} which allow to understand the Stokes phenomena working in the position domain. The same phenomena were described by Berry and Howls \cite{Berry_Howls} who noticed that divergent asymptotic expansions of thimble integrals encode the contribution of other critical values.
